Storm surge modelling in the Strait of Georgia

### 2014-10-02 RoughWork/manuscript.tex
Added images from new simulations. Began correcing text in Dec 2006 section

@@

Point Atkinson observed a maximum surge amplitude of 84 cm, which is approximately 20 cm higher than the model result, however the timing of the surge agrees almost exactly. The best agreement occurs at Victoria where the observed surge was 62 cm and the model returned 54 cm. At all of the locations, the model predicted the maximum surge to occur within 3.5 hours of the observed surge. Typically, the modelled surge was too early, in contrast to the later predictions in the Feb 4, 2006 case. Errors in the modelled water level at the time of maximum surge were of the same order as the errors in the surge amplitude.

The evolution and spatial distribution of the surge is highlighted in Figure \ref{fig:spatial} where the modelled residual is plotted every two hours beginning on Dec 14 at 18:30. The surge enters the system from the Strait of Juna de Fuca and Johnstone Strait, peaking between Dec 15 at 6:30 and Dec 15 at 10:30 and then begins to subside throughout the entire domain. Notably, the Strait of Georgia experiences the largest surge values, upwards of 70 cm, whereas the Juan de Fuca region experiences a maximum surge around 55 cm. Additionally, the coastal areas on the mainland side of the Strait of Georgia experience slightly higher surges than the Vancouver Island side, likely due to the southerly wind in the atmospheric model pushing water against the mainland coast.

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2006_spatial.pdf}
\caption{Propagation of the storm surge on Dec 14/15 2006. Modelled residual every 2 hours starting on Dec 14 at 18:30. Time advances from top left to bottom right. Note that the images are oriented with the numerical grid which is rotated $29^{\circ}$ counter-clockwise of North. }
\label{fig:spatial}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/nov2009_bg.pdf}
\caption{Wind and storm surge conditions at Point Atkinson for a strong wind event on Nov 19, 2009. Top: Wind speed from Environment Canada observations at Point Atkinson (solid) and from the atmospheric model (CGRF) at a grid point near Point Atkinson (dashed). Middle: Sea surface height anomaly at Tofino (solid) and Port Hardy (dashed) used as forcing conditions at the western and northern open boundaries. Bottom: Observed (solid) and modelled (dashed) residuals at Point Atkinson.  }
\label{fig:nov2009}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/tides.pdf}
\caption{Evaluation of model tidal amplitude and phases for the M$_2$ and K$_1$ constituents. }
\label{fig:tides}
\end{figure}

@@

Point Atkinson observed a maximum surge amplitude of 84 cm, which is approximately 29 cm higher than the model result, however the timing of the surge agrees almost exactly. as displayed in Figure \ref{fig:dec2006} The best agreement occurs at Victoria where the observed surge was 62 cm and the model returned 44 cm. At all of the locations, the model predicted the maximum surge to occur within 3.5 hours of the observed surge. Typically, the modelled surge was too early, in contrast to the later predictions in the Feb 4, 2006 case. Errors in the modelled water level at the time of maximum surge were of the same order as the errors in the surge amplitude.

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2006.pdf}
\caption{Comparison of observed water level and surge amplitudes during the Dec 15, 2006 storm surge simulation. }
\label{fig:dec2006}
\end{figure}%table instead of figure?

The evolution and spatial distribution of the surge is highlighted in Figure \ref{fig:spatial} where the modelled residual is plotted every hour beginning on Dec 15 at 05:30 UTC. The surge enters the system from the Strait of Juna de Fuca and Johnstone Strait, peaking between Dec 15 at 6:30 and Dec 15 at 10:30 and then begins to subside throughout the entire domain. Notably, the Strait of Georgia experiences the largest surge values, upwards of 70 cm, whereas the Juan de Fuca region experiences a maximum surge around 55 cm. Additionally, the coastal areas on the mainland side of the Strait of Georgia experience slightly higher surges than the Vancouver Island side, likely due to the southerly wind in the atmospheric model pushing water against the mainland coast.

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2006_spatial.pdf}
\caption{Propagation of the storm surge on Dec 15 2006. Modelled residual every hour starting on Dec 15 at 05:30 UTC. Time advances from top left to bottom right. Wind vectors from the atmopsheric forcing are overlaid in black.}
\label{fig:spatial}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2006_spatial_sshonly.pdf}
\caption{As in Figure \ref{fig:spatial} but for a simulation that does not include atmopsheric forcing. }
\label{fig:spatial_sshonly}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/nov2009.pdf}
\caption{Wind and storm surge conditions at Point Atkinson for a strong wind event on Nov 19, 2009. Top: Wind speed from Environment Canada observations at Point Atkinson (solid) and from the atmospheric model (CGRF) at a grid point near Point Atkinson (dashed). Middle: Sea surface height anomaly at Tofino (solid) and Port Hardy (dashed) used as forcing conditions at the western and northern open boundaries. Bottom: Observed (solid) and modelled (dashed) residuals at Point Atkinson.  }
\label{fig:nov2009}
\end{figure}
